---
title: 'Lab 7: multiple linear regression intro'
author: "Katie Munster"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore penguins

Use `GGally::ggpairs()` to create a pairs plot.

```{r}
ggpairs(penguins)
```

That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot:

- species
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% #range of columns using colon
  ggpairs(aes(color = species)) #ggpairs is a wrapper around ggplot. can use typical things from ggplot
```

## Multiple linear regression

We are going to try to understand (a bit better) relationship between multiple predictor variables and an outcome which is penguin body mass.

The different predictor variables we're going to try are:

- species
- flipper length
- sex
- bill depth

### Model 1

Model body mass based on only flipper length and bill depth
(bad idea... there are important variables missing, ie. sex and species)
```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Call model by name to return only coefficients:
model_1

# More information on the coefficients and model:
summary(model_1)
```

If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average. # Use in line code, do not write out values!!!

R-squared value: 76% of variants in penguin body mass is explained by this model (penguin flipper length and bill depth).

Actually -- we think a model for penguin body mass should contain variable species, flipper length, and penguin sex.

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

# Let's check out the coefficients:
model_2

# The reference level for species is Adelie and the reference level for penguin sex is female. We interpret the coefficients with respect to the reference level.

# Try interpreting the coefficients for:
# flipper length, Gentoo, and male

# If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increase by 20.02 g, on average.

# On average we expect a Gentoo penguin to be 836.26 g larger than an Adelie penguin that are otherwise similar.

# On average we expect a male penguin to be 530.38 g larger than a female penguin that are otherwise similar.
```

## Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~ sex)
```

## A couple ways to get and report MLR model outcomes

Use broom::tidy() to get model coefficient info in a tidy data frame.

```{r}
penguin_model2_coef <- tidy(model_2)

penguin_model2_coef
```

Try to write inline code `r` that spits out the coefficient for Gentoo.

The coefficient for Gentoo penguin is `r penguin_model2_coef$estimate[4]`.

## Look at model diagnostics

Use the plot() function.

```{r}
plot(model_2)
# residuals are normally distributed
# no concerns about do MLR

summary(model_2)
# Adjusted R-squared value has increased when we added multiple variables
```

## Report the model outputs in a summary table

Use modelsummary:
```{r}
modelsummary(model_2)
```

Use stargazer:
```{r, results = "asis"}
# when using stargazer, do that so it knows the output is already in the html

stargazer(model_2, model_1, type = "html")
# look at results in html

# stargazer is a regression model output tool
# customize it
```




